---
title: "intrinoR"
author: "Bruce C. Schardt"
date: "7/2/2019"
output: md_document

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## intrinoR

An R language wrapper for the [INTRINO](https://intrino.com) market data Api.

You will need an account and api keys, [signup](https://intrinio.com/signup) for a free starter account.

## Installation

To install as a dependancy into your project at the R REPL command prompt

```r
install.github("schardtbc/intrinoR")
```

then in your .env or .Renviron file add the following keys

```
INTRINO_BASE_URL = "https://api-v2.intrinio.com"
INTRINO_PRODUCTION_KEY  = "your production key here"
INTRINO_SANDBOX_KEY = " your sandbox key here"
INTRINO_API_VERSION = "v2"

# use production and snadbox keys from your intrino account
# make sure the .env file is in your .gitignore file
# do not hard code the keys into your application code
# do not upload the keys to github.
# you can easily change the keys at intrino.com if they become compromised
```

[Api documentation](https://docs.intrinio.com/documentation/api_v2/getting_started) documentation.


## Usage Example

```{r}
library(intrinoR)
useSandbox()
# useProduction()

res <- getSecurityStockPrices("AAPL", opts = list(start_date = "2019-01-01"))
res
```

### Companies
|     | Endpoint                                      | function call              |
|-----|:----------------------------------------------|:-------------------------------------------------------------------|
| [X] | /companies                                    | [`getAllCompanies`](/doc/getAllCompanies.md)                       |
| [ ] | /companies/search                             |                                                                    |
| [X] | /companies/{identifier}                       | [`getCompany`](/doc/getCompany.md)                                 |
| [X] | /companies/{identifier}/securties             | [`getCompanySecurities`](/doc/getCompanySecurities.md)             |
| [X] | /companies/{identifier}/news                  | [`getCompanyNews`](/doc/getCompanyNews.md)                         |
| [X] | /company/{identifier}/fundamentals            | [`getCompanyFundamentals`](/doc/getCompanyFundamentals.md)         |
| [X] | /company/{identifier/filings}                 | [`getCompanyFilings`](/doc/getCompanyFilings.md)                   |
| [X] | /company/{identifier}/data_point/{tag}/number | [`getCompanyDataPointNumber`](/doc/getCompanyDataPointNumber.md)   |
| [X] | /company/{identifier}/data_point/{tag}/text   | [`getCompanyDataPointText`](/doc/getCompanyDataPointText.md)       |
| [X] | /company/{identifier}/historical_data/{tag}   | [`getCompanyDataPointHistory`](/doc/getCompanyDataPointHistory.md) |

### Securities
|     | Endpoint                                      | function call              |
|-----|:----------------------------------------------|:-------------------------------------------------------------------|
| [X] | /securities                                   | [`getAllSecurities](/doc/getAllSecurities.md)                      |
| [X] | /securities/{identifier}                      | [`getSecurityById`](getSecurityById.md)                            |
| [X] | /securities/{identifier}/prices               | [`getSecurityStockPrices`](getSecurityStockPrices.md)              |
| [X] | /securities/{identifier}/prices/realtime      | [`getSecurityRealtimePrice`](getSecurityRealtimePrice.md)          |
| [X] | /securities/{identifier}/prices/intraday      | [`getSecurityIntradayPrices`](getSecurityIntradayPrices.md)        |
| [X] | /securities/{identifier}/dividends/latest     | [`getSecurityDividendsLatest`](getSecurityDividendsLatest.md)      |
| [X] | /securities/{identifier}/earnings/latest      | [`getSecurityEarningsLatest`](getSecurityEarningsLatest.md)        |
| [X] | /securities/{identifier}/zacks/analyst_ratings/snapshot | [`getSecurityZacksAnalystRatingsSnapshot`](getSecurityZacksAnalystRatingsSnapshot.md) |

